An event-sourced and decentralized database with IPLD and materialized views

### 2019-09-27 draft.tex
clarify
Signed-off-by: andrew <andrew@textile.io>

Therefore, solutions such as \texttt{ipfs-log} include a built-in CRDT to manage conflicts not resolved by the Merkle-Clock. This approach works for many cases, but the use of a deterministic resolution strategy can be insufficient in cases where complicated data structures or long chains of missed events need to be reconciled. A git merge highlights one such example, in which a predetermined merge strategy can be used, but is not often the best choice in practice. Furthermore, a multi-writer log using a linked data format (e.g., a Merkle-Dag) in imperfect networking or storage environments can lead to suboptimal states where it may exceedingly costly (networking, storage, and computation) to regain consistency.

>>>>

Therefore, solutions such as \texttt{ipfs-log} include a built-in CRDT to manage conflicts not resolved by the Merkle-Clock. This approach works for many cases, but the use of a deterministic resolution strategy can be insufficient in cases with complicated data structures or complicated network topologies. A git merge highlights one such example, in which a predetermined merge strategy can be used, but is not often the best choice in practice. Furthermore, a multi-writer log using a linked data format (e.g., a Merkle-Dag) in imperfect networking or storage environments can lead to suboptimal states where it may exceedingly costly (networking, storage, and computation) to regain consistency.
